Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2016-02-06 WSSSPE3/report/WSSSPE3_review.tex
A few more changes that seem to make sense.
abstract updates

\begin{abstract}
This technical report records and discusses the Third Workshop on Sustainable
Software for Science: Practice and Experiences (WSSSPE3). The report includes a
description of the keynote presentation of the workshop, which served as an overview of sustainable
scientific software. It also summarizes a set of lightning
talks in which speakers highlighted to-the-point lessons and challenges
pertaining to sustaining scientific software. Lastly, the report focuses on the
discussions, future steps, and future organization for a set of self-organized
working groups on topics including developing pathways to funding scientific
software; constructing useful common metrics for crediting software
stakeholders; identifying principles for sustainable software engineering
design; reaching out to research software organizations as a global effort;
building communities for software sustainability. For each group, we include a
point of contact and a landing page that can be used by those who want to join
that group's future activities. The main challenge left by the workshop is to
see if the groups will execute these activities that they have scheduled, and
how the WSSSPE community can encourage this to happen.

@@

\appendix
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Organizing Committee}  \label{sec:orgcom}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\todo{Do we want email addresses here?}

>>>>

\begin{abstract}
This technical report records and discusses the Third Workshop on Sustainable
Software for Science: Practice and Experiences (WSSSPE3). The report includes a
description of the keynote presentation of the workshop, which served as an overview of sustainable
scientific software. It also summarizes a set of lightning
talks in which speakers highlighted to-the-point lessons and challenges
pertaining to sustaining scientific software. The final and main contribution of the report is a summary of the
discussions, future steps, and future organization for a set of self-organized
working groups on topics including developing pathways to funding scientific
software; constructing useful common metrics for crediting software
stakeholders; identifying principles for sustainable software engineering
design; reaching out to research software organizations around the world; and
building communities for software sustainability. For each group, we include a
point of contact and a landing page that can be used by those who want to join
that group's future activities. The main challenge left by the workshop is to
see if the groups will execute these activities that they have scheduled, and
how the WSSSPE community can encourage this to happen.

@@

\newpage
\appendix
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Organizing Committee}  \label{sec:orgcom}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\todo{Do we want email addresses here?}
